### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

\stitle{(2) Localization with affected balls (\affballsx)}.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computing and updating match relations for all balls.

@@

\etitle{(1) Identifying \affballsx}.
Algorithm \inc invokes two different procedures to identify \affballsx for separate $\Delta P$ or $\Delta G$, respectively.
For  simultaneous $\Delta P$ and $\Delta G$, \inc takes the union of the \affballsx produced by  the two procedures.

\etitle{(2) Update partial match relations in \affballsx}.
For a ball affected by $\Delta P$, \inc updates the partial match relations for the updated pattern fragments with incremental computation;
For a ball affected by $\Delta G$, \inc updates the partial match relations for all pattern fragments;
And, for a ball affected by both $\Delta P$ and $\Delta G$, \inc follows the same way as $\Delta G$ only.
Meanwhile, auxiliary structure \fb (to be seen shortly) is updated for handling continuous separate and simultaneous pattern and data updates.

\etitle{(3) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
	\begin{center}
		\subfigure{\label{fig-auxstr-index}
			\includegraphics[scale=0.585]{./fig/fig-auxstr-index.eps}}
		\subfigure{\label{fig-inc-maintain-unit}
			\quad\quad \vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-unit.eps}}
		\subfigure{\label{fig-inc-maintain-batch}
			\vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-batch.eps}}
		\vspace{-3ex}
		\caption{Example auxiliary data structures}
		\label{fig-auxiliary-structures}
		\vspace{-3ex}
	\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\stitle{(2) Localization with affected balls (\affballsx)}.
We further localize the impact of pattern and data updates  with {\em affected balls} to avoid unnecessary computations.

@@

\etitle{(i) Identifying \affballsx}.
Algorithm \inc invokes two different procedures to identify \affballsx for separate $\Delta P$ or $\Delta G$, respectively.
For  simultaneous $\Delta P$ and $\Delta G$, \inc takes the union of the \affballsx produced by  the two procedures.

\etitle{(ii) Update partial match relations in \affballsx}.
For a ball affected by $\Delta P$, \inc updates the partial match relations for the updated pattern fragments with incremental computation;
For a ball affected by $\Delta G$, \inc updates the partial match relations for all pattern fragments;
And, for a ball affected by both $\Delta P$ and $\Delta G$, \inc follows the same way as $\Delta G$ only.
Meanwhile, auxiliary structure \fb (to be seen shortly) is updated for handling continuous separate and simultaneous pattern and data updates.

\etitle{(iii) Combining partial match relations}. \inc combines all partial relations for a subset of \affballsx and computes the top-$k$ perfect subgraphs within them and their inner balls.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[tb!]
	\begin{center}
		\subfigure{\label{fig-auxstr-index}
			\includegraphics[scale=0.585]{./fig/fig-auxstr-index.eps}}
		\subfigure{\label{fig-inc-maintain-unit}
			\quad\quad \vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-unit.eps}}
		\subfigure{\label{fig-inc-maintain-batch}
			\vrule \quad\quad
			\includegraphics[scale=0.585]{./fig/fig-inc-maintain-batch.eps}}
		\vspace{-2ex}
		\caption{Example auxiliary data structures}
		\label{fig-auxiliary-structures}
		\vspace{-4ex}
	\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
